Twists of supersymmetric gauge theories

### 2019-05-06 paper.tex
merge

\begin{dfn}
A {\bf classical field theory} is a free classical field theory $(E, Q, \omega)$ equipped with a functional
\[
I \in \oloc^+(E)
\]
satisfying the classical master equation 
\[
Q I + \frac{1}{2} \{I,I\} = 0 .
\]
\end{dfn}

@@

% spinorial representations, supertranslation groups, superPoincar\'{e} groups
% list possible massless supermultiplets in dimensions [4, 10] with <= 16 supercharges
% explain what a supersymmetric field theory is (in terms of the L_infinity action of the supertranslation algebra)

\brian{How we we feel about using $L$ for the local Lie algebra of BRST fields and $\fL$ for the BV fields?}

\subsection{Supersymmetric twisting}

@@

The matter sector of the theory is labeled by the BRST fields:
\begin{itemize}
\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
\end{itemize} 
which together define the (abelian) local Lie algebra
\[
L_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
\]
\subsection{Dimension 3}

>>>>

\brian{recall dfn of $\oloc$ of a gr vb.}

\begin{dfn}
A {\bf classical field theory} is a free classical field theory $(E, Q, \omega)$ equipped with a functional
\[
I \in \oloc^+(E)
\]
of cohomological degree zero satisfying the classical master equation 
\[
Q I + \frac{1}{2} \{I,I\} = 0 .
\]
\end{dfn}

\begin{remark}
There is a super variant of the above two definitions. 
A $\ZZ/2$ graded field theory is a $\ZZ \times \ZZ/2$ graded vector bundle $E$ equipped with the same additional data as above.
We require that $Q, \omega, I$ all have even parity with respect to the additional $\ZZ/2$ grading. 
\end{remark}

@@

% spinorial representations, supertranslation groups, superPoincar\'{e} groups
% list possible massless supermultiplets in dimensions [4, 10] with <= 16 supercharges

\subsubsection{Supersymmetric field theory}

% explain what a supersymmetric field theory is (in terms of the L_infinity action of the supertranslation algebra)

\begin{dfn}
Let $(E,Q,\omega, I)$ be a $\ZZ/2$-graded classical field theory on $\RR^n$. 
A {\em strict action} of a super Lie algebra $\fg$ on $(E,Q,\omega, I)$ is a map of super dg Lie algebras
\[
\rho : \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\em action} is an $L_\infty$ map of super dg Lie algebras
\[
\rho : \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
\end{dfn}

\begin{rmk}
More generally, one can speak of what it means for a 
\subsection{Supersymmetric twisting}

@@

The matter sector of the theory is labeled by the BRST fields:
\begin{itemize}
\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
\end{itemize} 
which together define the (abelian) local Lie algebra
\[
\sE_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
\]
\subsection{Dimension 3}
